sdmTMB: an R package for fast, flexible, and user-friendly generalized linear mixed effects models with spatial and spatiotemporal random fields

### 2023-02-02 doc/paper-jss/pcod.Rmd
Update for sdmTMBextra

We can inspect simulated residuals from the DHARMa package (Fig.\ \ref{fig:sim-resids}).

```{r sim-resids, out.width="4in", warning=FALSE, results='hide', cache=TRUE, echo=TRUE, fig.cap="Simulated residuals from the DHARMa package.", fig.pos='ht', fig.align='center'}
set.seed(123)
simulate(fit, nsim = 500) %>%
  dharma_residuals(fit)
```

@@

```{r mcmc-resids, warning=FALSE, results='hide', cache=TRUE}
set.seed(123)
r <- residuals(fit,
  type = "mle-mcmc", 
  mcmc_iter = 200, mcmc_warmup = 100
)
```

>>>>

We can inspect randomized quantile residuals calculated with predictions that used the Laplace approximation:

```{r}
set.seed(123)
r <- residuals(fit)
```

@@

```{r mcmc-resids, warning=FALSE, results='hide', cache=TRUE}
set.seed(123)
post <- sdmTMBextra::predict_mle_mcmc(fit, mcmc_iter = 200, mcmc_warmup = 100)
r <- residuals(fit, mcmc_samples = post, type = "mle-mcmc")
```
